\documentclass[11pt,a4paper]{article}
\usepackage[utf8x]{inputenc}
%\usepackage{isolatin1}
\usepackage{ctable}
\usepackage[french]{babel}

%\usepackage[T1]{inputenc}
%\usepackage{float}
%\usepackage{vmargin}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{graphics}

\setlength{\parindent}{10pt}
\setlength{\parskip}{10pt}
%\renewcommand{\baselinestretch}{2.0}
%\renewcommand\baselinestretch{1.5}
\newcommand\numero{{n$^{\rm o}\,\,$}}
\input{macros}
%\input{nondim}

\begin{document}
\titlepage
\mbox{}
\begin{center}
\vskip 1cm
{\Large \bf Outflow
}\\\vskip 1cm
Stéphane Zaleski\\
\vskip 0.5cm
\today
\end{center}

Following the Book
$$
\partial u_n / \partial n = 0 
$$ 
Together with the incompressibility equation this implies
$$
\int_{S_{out}} u . n ds = \int_{S_{in}} u . n ds 
$$
on the exit surface $S_{out}$ but this is not satisfied by the ghost velocity on the exit face. 
If on the entry face u . n = U_in then in the projection method
one must set $\partial p / \partial n = 0$ on S_in, then 
$$
\int div (1/rho) grad p dv = \oint  (1/rho) grad p . ds
$$
and thus 
$$
\int div (1/rho) grad p dv = \int_S_out  (1/rho) grad p . n ds
$$
on the exit surface S.
Consider the simplest setup, akin to standard "wall" conditions, where
u=u_in is fixed on S_in and u=u_out is fixed on S_out with u_in S_in =
u_out S_out

On the exit face
a) either pressure is set at ghost points: p(ie+1)=P_out and then the
pressure equation at p(ie) is solved to obtain incompressibility at
index ie. Is u(ie+1/2) is computed ? recall index ieu = ie-1 if bdry_cond
 not periodic so ie is indeed not computed. But u(ie+1/2) could be extrapolated.

b) or u(ie+1/2) is set , for instance by extrapolation +
``correction of the mass flux'' (the meaning of ``correction of the mass
flux is given below''), and then u(ie+1/2) is not pressure corrected so
p(ie+1) = p(ie) and A_East = 0 and no pressure value is set. 

In case b), since p(ie+1) = p(ie) , then $\partial p / \partial n = 0$ and 
$$
\int div (1/rho) grad p dv = \int_S_out (1/rho) grad p . n ds = 0 
$$
so the solvabity condition is 
$$
\oint div (1/rho) grad p dv = \int div u^* dv = 0 
$$
which is the standard case which we know works. The solvability condition  is
ensured by correction of the mass flux for u^*. The correction of the mass flux is non-zero 
because div u^* is in general not zero (otherwise the pressure correction method
would not be necessary) . ``Correction of the mass flux'' means that an average outflow
velocity is computed
$$
\bar u_in = = (1/S_in) \int u_in ds
\bar u^*_out = = (1/S_out) \int u^*_out ds
$$
and after correction
$$
u^**_S_out = u^*_S_out - \bar u^*_out + \bar u^*_in
$$
In discrete terms, S_out is the surface ie+1/2 and u^*(ie+1/2) is first computed by 
extrapolation at first order
$$
 u^*(ie+1/2) =  u^*(ie-1/2) 
$$
In case a) let u^*(ie+1/2) be extrapolated but not corrected for the mass flux. 
The pressure correction is applied  to ensure incompressibility. The Poisson equation
has boundary condition p=P_out on S_out and $\partial u_n / \partial n = 0$
on S_in. Then we need proof that this is well posed. 

Attempt case a) as BC 5 and case b) as BC 4. 

\end{document}
